%-------------------------
% Resume in Latex
% Author : Abey George
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Pradeep Kumar} \\ \vspace{1pt}
    New Delhi, Delhi \\ \vspace{1pt}
    \small   \href{mailto:pradeepkumarbgs62019@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{pradeepkumarbgs62019@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/pradeep-sahu-180b3423a/}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{linkedin}}  ~
    \href{https://github.com/pradeepbgs}{\raisebox{-0.2\height}\faGithub\ \underline{github}} ~
    \vspace{-8pt} \\
    \vspace{18pt}
    Hello, I'm Pradeep Kumar Sahu, a Software Developer with a strong foundation in web technologies. \\ 
    I recently graduated and am passionate about coding and building scalable web applications. My expertise lies in full stack development, Mobile Application Development with React Native.
    \vspace{-8pt}
\end{center}



%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SBSS College  }{ 2021 --  2024}
      {  \textbf{} \textbf{}}{Begusarai, Bihar}
  \resumeSubHeadingListEnd
  

%------RELEVANT COURSEWORK-------
\section{TECHNICAL SKILLS}
 \vspace{3pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{ \normalsize{ JavaScript/TypeScript , Python , SQL, Java/Golang (learning and exploring)}} \\

     \textbf{\normalsize{Developer Tools:}}{ \normalsize{ Git , GitHub , Docker , Nginx , Postman }} \\
     
     \textbf{\normalsize{Technologies/Frameworks:}}
     {\normalsize{ ReactJS, VueJS, NextJS, NodeJS Backend, Spring Boot, Django, Flask }} \\

     \textbf{\normalsize{Databases:}}
     {\normalsize{ PostgreSQL, MongoDB, Redis, Firebase Realtime Database }} \\

     \textbf{\normalsize{Android Development:}}{ \normalsize{ React Native with Expo }} \\

     \textbf{\normalsize{System Design:}}{ \normalsize{ Learning High-Level System Design concepts including scalability, load balancing, and distributed systems }} \\
    }}}
 \end{itemize}


    
    
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{PROJECTS}
\vspace{-5pt}
    \resumeProjectHeading
          {\href{https://github.com/pradeepbgs/PingFile}{\textbf{\large{\underline{PingFile CLI}}} \href{https://github.com/pradeepbgs/PingFile}{
           \href{https://github.com/pradeepbgs/PingFile}{\raisebox{-0.2\height}\faGithub\ \underline{}} ~\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{A Command-Line Tool for API Testing and Execution}}}{}
           \vspace{-5pt}
         \resumeItemListStart
\resumeItem{\normalsize{
    \textbf{PingFile CLI} is a command-line tool designed to simplify API testing and execution by allowing users to run API requests directly from configuration files in \textbf{JSON}, \textbf{YAML}, or \textbf{PKFILE} formats.
}}
\resumeItem{\normalsize{
    \textbf{Key Features:}
    \begin{itemize}[leftmargin=0.25in, label={}]
        \item Supports multiple file formats (\textbf{JSON}, \textbf{YAML}, \textbf{PKFILE}) for defining API requests.
        \item Provides colorful terminal output with detailed status codes, headers, and response bodies.
        \item Allows saving API responses and supports multithreaded execution for batch processing.
        \item Includes advanced features like cookie management, credential handling, and file uploads.
    \end{itemize}
}}
\resumeItem{\normalsize{
    \textbf{Impact:} Simplifies API testing workflows for developers by providing a lightweight, cross-platform tool that integrates seamlessly into development pipelines.
}}
\resumeItemListEnd

    \vspace{-5pt}
    \resumeProjectHeading
          {\href{https://github.com/pradeepbgs/diesel}{\textbf{\large{\underline{Diesel.js}}} \href{https://github.com/pradeepbgs/diesel}{
           \href{https://github.com/pradeepbgs/diesel}{\raisebox{-0.2\height}\faGithub\ \underline{}} ~\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{A fast , minimilistic web framework for building robust & fast APIs  }}}{}
           \vspace{-5pt}
         \resumeItemListStart
\resumeItem{\normalsize{\textbf{Diesel.js} is a high-performance, Bun.js-based web framework with Express-like syntax, built for rapid API creation. It supports lazy parsing, dynamic routing, and efficient middleware execution to enhance speed and reduce runtime overhead.}}
\resumeItem{\normalsize{Features include \textbf{Route Security} with the \texttt{filter()} method for managing public and protected routes, enabling fine-grained access control via \texttt{permitAll()} and \texttt{require()} functions, and custom JWT-based authentication for sensitive endpoints.}}
\resumeItem{\normalsize{Diesel.js also supports \textbf{Lifecycle Hooks} (e.g., \texttt{onRequest}, \texttt{preHandler}, \texttt{postHandler}, \texttt{onSend}) to execute custom logic such as logging, authentication, and data handling at various stages of the request lifecycle.}}
\resumeItemListEnd

          
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
       \resumeProjectHeading
          {\href{https://github.com/pradeepbgs/DevTube-backend}{\textbf{\large{\underline{DevTube}}} \href{Project Link}{
          \href{https://github.com/pradeepbgs/DevTube-backend}{\raisebox{-0.2\height}\faGithub\ \underline{}}\raisebox{-0.1\height}\faExternalLink }} $|$ \large{\underline{Recat , Express.js , MongoDB with Aggregation pipeline}}}{}
          \vspace{-5pt}
          \resumeItemListStart
\resumeItem{\normalsize{About Project: \textbf{DevTube is a video-sharing platform where users can authenticate and access personalized features.}}}
\resumeItem{\normalsize{\textbf{Users can upload and watch videos, like and subscribe to channels, and comment on videos.}}}
\resumeItem{\normalsize{\textbf{Includes social sharing features like tweet functionality for easy video sharing.}}}
\vspace{10pt}
\resumeItemListEnd

          \vspace{-13pt}
          
    \resumeSubHeadingListEnd
\vspace{12pt}

%




 


\end{document}